Corotating Dust Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-01 paper/ms.tex
update ms

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}

@@

@@

\begin{itemize}
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample seem to remain fixed over the span of available
    observations, the light curve shapes themselves evolve, similar to
    rotating stars.
	%
  \item The same CQV can show dips with very similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of the fundamental period,
    sometimes simultaneous, and each lasting for up to 50 cycles.
	%
  \item The CQV phenomenon persists for at least 150\,Myr, based on
    the existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.  It
    may extend to even older ages, however the lack of detected CQVs
    in the Hyades and Praesepe suggest that the phenomenon is unique
    to the pre-main-sequence for M-dwarfs.
	%
  \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles.
	%
  \item The population-averaged duty cycle for CQVs seems to be
    $\approx 75$\%, based on the fraction of bonafide CQVs that
    ``turned off'' during TESS re-observations.
\end{itemize}

@@

{\bf author contribution statement goes here}
L.G.B.~and R.~J. conceived the project and executed the
dip-based and Fourier-based searches, respectively.
L.G.B.~drafted the initial manuscript, and performed the cluster
membership analysis.
S.~R. and R.~J. vetted the results from the Fourier search.
L.A.H.~advised on project scope and experiment design.
All authors assisted in manuscript revision.

@@

>>>>

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}
\newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

@@

\author[0000-0001-7204-6727]{G\'asp\'ar \'A. Bakos}
\affiliation{\princeton}

@@

\begin{itemize}
	%
  \item CQVs are quasiperiodic.  While the mean periods in our
    sample seem to remain fixed over the span of available
    observations, the light curve shapes themselves evolve, similar to
    rotating stars.
	%
  \item The same CQV can show dips with very similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of the fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles.
	%
  \item The CQV phenomenon persists for at least 150\,Myr, based on
    the existence of CQVs in AB Dor, the Pleiades, and Psc-Eri.  It
    may extend to even older ages, however the lack of detected CQVs
    in the Hyades and Praesepe suggests that the phenomenon does become
    less common at older ages.
	%
  \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles.
	%
  \item The population-averaged duty cycle for CQVs seems to be
    $\approx 75$\%, based on the fraction of bonafide CQVs that
    ``turned off'' during TESS re-observations.
\end{itemize}

@@

%{\bf author contribution statement goes here}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
GAB acquired and maintained the servers used to run the dip-finding
pipeline.
All authors assisted in manuscript revision.

@@

\section{More river plots}

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_0_650_vmin-0.06000_vmax0.06000.png}
			\includegraphics[width=0.43\textwidth]{TIC300651846_river_seismic_2305_2630_vmin-0.06000_vmax0.06000.png}
		}
	\end{center}
	\vspace{-0.4cm}
	\caption{
		{\bf River plots of TIC 300651846}.
		The envelope has not been subtracted.
		7 sectors of continuous 2-minute observations.  (Thanks to DDT029)
	}
	\label{fig:lpriver0}
\end{figure*}
